|

### 2023-02-16 paper.Rmd
Thu Feb 16 15:00:07 CET 2023: update-remote.sh

\setcounter{page}{1}

@@

```{=tex}
\thispagestyle{empty}
\newpage
\listoftables
\listoffigures
\thispagestyle{empty}
\newpage
```
<!--Markdown Text -->

@@

DAE-LSTMs are artificial neural networks that can be trained in an unsupervised learning environment to minimize a reconstruction error for encoding input data into a compressed representation and subsequently decoding the compressed representation back to the input dimension.
In DAE-GP, DAE-LSTMs are trained with a subset of high-fitness solutions selected from a parent population with the aim to capture their promising qualities.
The resulting model is then used to sample new offspring solutions by propagating partially mutated solutions from the parent population through the DAE-LSTMS [@dae-gp_2020_rtree].
In previous work DAE-GP has been shown to outperform GP for both a generalized version of the royal tree problem [@dae-gp_2020_rtree] as well as for a real-world symbolic regression problem [@dae-gp_2022_symreg].

@@

```{r statutory_declaration, echo=FALSE, fig.align = 'center', out.width='500px'}
knitr::include_graphics("~/masterThesis/master_thesis/private/statutory_declaration_signed.pdf")
```

>>>>

\setcounter{page}{2}

@@

```{=tex}
\thispagestyle{empty}
\newpage
\listoftables
\thispagestyle{empty}
\newpage
\listoffigures
\thispagestyle{empty}
\newpage
```
<!--Markdown Text -->

@@

DAE-LSTMs are artificial neural networks that can be trained in an unsupervised learning environment to minimize a reconstruction error for encoding input data into a compressed representation and subsequently decoding the compressed representation back to the input dimension.
In DAE-GP, DAE-LSTMs are trained with a subset of high-fitness solutions selected from a parent population with the aim to capture their promising qualities.
The resulting model is then used to sample new offspring solutions by propagating partially mutated solutions from the parent population through the DAE-LSTM [@dae-gp_2020_rtree].
In previous work DAE-GP has been shown to outperform GP for both a generalized version of the royal tree problem [@dae-gp_2020_rtree] as well as for a real-world symbolic regression problem [@dae-gp_2022_symreg].

@@

```{r statutory_declaration, echo=FALSE, fig.align = 'center', out.width='500px'}
knitr::include_graphics("~/masterThesis/master_thesis/private/statGood.pdf")
```
